---
title: "Advanced bioinformatics 9522"
date: "May 8, 2020"
output: html_document
---

## Task 1

```{r}
sum(5:55)
```
sum() is r-builtin function which takes vector as input and outputs sum of all elements in the vector. Using :operator I could create a vector that includes all integers from 5 to 55

## Task 2

```{r}
sumfun<-function(n){
  sum(5:n)
}
sumfun(10)
sumfun(20)
sumfun(100)
```
sumfun function takes argument n and calculate sum of all integers between 5 to n.


## Task 3
```{r}
number_of_entries <- 12
fibonacci <- numeric(number_of_entries)
fibonacci[1] <- 1
fibonacci[2] <- 1
for (i in 3:number_of_entries) { 
   fibonacci[i] <- fibonacci[i-1]+fibonacci[i-2]
}
fibonacci
```
Fibonacci series is calculated as the sum of the two preceding members of the sequence, where the first two steps in the sequence are 1, 1. 
Creating for loop we iterate over the fibonacci vector (length of 12) and each time assign new value by summing last two  numbers.


## Task 4

```{r}
library(ggplot2)
data("mtcars")
ggplot(mtcars,aes(as.factor(gear),mpg,fill = as.factor(gear)))+geom_boxplot()+labs(title = "Mile per galon per vs Gear",x="Number of Gear",y="Mile per galon",fill = "Gear colors")


```
ggplot is library which is used to make plots. Here is boxplot and we see that mile per galon is different by geear


## Task 5
```{r}
data(cars)
model<-lm(speed~dist, data = cars)
summary(model)
```
The command lm() is used to find linear relationship between variables we provide.
The intercept and slope between the variables are outputs of the function.
The intercept and of the linear model is 8.28 with 0.87438 standard error  and the slope is 0.16 with 0.01749 error. There are 2 features in the dataset 


## Task 6
Use ggplot to plot the data points from Task 6 and the linear fit.

```{r}
ggplot(cars,aes(dist,speed))+geom_point()+geom_smooth(method='lm',se=F)+ggtitle("Linear relationship Speed vs Distance")


```
geom_smooth function from ggplot fits line using linear model's slope and intercept.


## Task 7
```{r}
cars$ft_per_second<-((cars$speed*5280)/3600)
model <- lm(dist~ft_per_second**2,data=cars)
summary(model)
```
Speed was given  mile per hour as it is required to do analysis for for seconds and with distance. I created new feature ft_per_second by multiplying vector with 5280 to get fits and divided it into 3600 to get seconds. Afterwards, conducted linear regression where dist feature is dependent variable and ft_per_second is independent.
R-square is 0.64 which means our model explains 64% of variation in dependent variable. And one unit increase in speed per second increases necessary distance  to have by 2.6812.





